State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-26 prism-backend/research/soa_review/gs.tex
Review of FHS19.
Some writeup on ACs main approaches, security models, and functionality. Doc reorg.
Polished version. Still early draft, but at least readable (excluding DAA section, which is not a priority for now).

\paragraph{Main intuition.}
%
Group signatures were first proposed by Chaum and van Heyst in 1991 \cite{ch91}
as a privacy-respectful extension to conventional digital signatures.
The intuition is simple: in order to avoid revealing the identity of the signer,
we make her signatures look indistinguishable to the signatures of all other
members of a group. Then, any entity with access to the group public key can
verify that a group signature comes from a member of the group, but cannot
tell which specific one actually created it.
%
Beyond this, group signature schemes have one main feature: a (set of) group
manager(s) control who can become a member of the group. Also, most frequently,
a (set of) group manager(s) decide when to expell a member from the group, or
when to re-identify the creator of a specific signature.
%
The initial idea put forward in \cite{ch91} had, as is to be expected, a number
of limitations. In the following years, the seminal work was extended, both
formally, functionally and efficiency-wise.

@@

\subsubsection{Main approaches.}
%
There are two main ways that are recurrently used to instantiate group signature
schemes: \emph{Sign-Encrypt-Prove} and \emph{Sign-Randomize-Prove}. In both
variants, when new members of the group join, they receive a credential (i.e.,
a signature by the issuer) derived from a secret they choose. Then, when
creating a group signature, they prove control a valid credential and the
associated secret. The difference lies on how this credential is kept hidden
from the verifier.
%
In the sign-encrypt-prove variant, proposed in \cite{bmw03}, signers
encrypt their credential with a \doubt{IND-CCA2? what type?} scheme and then
create a NIZK \needcite proof of knowledge of such a valid credential
over their secret (plus the message they want to sign). This typically results
in schemes with more efficient openings, as the opening authority just has
to decrypt the encrypted credential. However, group signatures require more
space.
%
In the sign-randomize-prove variant, proposed in \needcite \todo{Get Shorty?},
credentials are actually randomizable signatures by the issuer. Signers then
randomize the signature (credential), and create a NIZK proof of knowledge that
this credential is issued for a secret they know (again, plus the message
they want to sign). This usually results in schemes with less efficient openings,
as the opening authority needs to iterate over the registered credentials until
finding the one from which the randomized credential was derived. However, the
produced group signatures are also shorter.

@@

\subsubsection{Main security models.}
%
Security for group signatures is given in the form of game-based definitions
\needcite.
The first formal security model appeared in \cite{bmw03}. It captured security
for groups with a prefixed set of members, added by the group manager upon the
creation of the group. This static requirement was too restrictive to be
realistic, and was quickly extended in \cite{bsz05} and \cite{kty04,ky06}, to
model that new users can join the group after it has been created. The models
in \cite{bsz05,kty04,ky06} are usually referred to as dynamic or partially
dynamic. \cite{bcc+16} generalizes the (partially) dynamic setting into a fully
dynamic model, which considers extra desirable security properties when users
can be revoked (i.e., removed from the group).

@@

\paragraph{Forward security.}
Forward security aims at restricting the impact of security compromises (e.g.,
key leakage) to the future: i.e., if an attacker gains control of a user's
private key, only signatures produced after the compromise should be considered
invalid. In schemes that do not ensure forward secrecy, such a compromise also
renders invalid signatures produced before the compromise. Note that, for
conventional signatures, only the compromised users is (directly) affected by
such event. However,  in group signatures, all group members are directly
affected, as the signer's identity is not revealed by the signature. Thus,
in order to learn whether or not a past signature was issued by a compromised
user, it is necessary to resort to the opener -- therefore, reidentifying
\emph{all} users in the system.
%
Forward security has been introduced in group signatures in works like
\cite{song01,ly12} \needcite.
%
Interestingly (but logically), the approach to incorporate this property
holds similarities with the functionality to implement fully dynamic group
signatures: for forward security, users are usually required to apply an
update procedure to their private keys \cite{ly12}; in fully dynamic group
signatures, it is the group manager (or the opener) who has to update some
key material \cite{bcc+16}. In both cases, time has to be discretized in epochs,
and conditions are introduced into the security properties that prevent an
adversary being able to deanonymize (produce) a valid signature generated
(using) a key in an epoch in which such key was not supposed to be active
(either because the user updated it -- in a forward secure scheme -- or the
group manager revoked it -- in a fully dynamic scheme).

\paragraph{Revocation mechanisms.}
Verifier Local Revocation \cite{bs04}, accumulators approach.

@@

\begin{itemize}
\item Size of (group) keys.
\item Size of signatures.
\item Verification time (batching, including revocation checks...)
\item Accumulators.
\end{itemize}

\subsubsection{Main challenges.}

@@

GS-MDO imply IBE \cite{ehk+19}.
GS are implied (shouldn't his by imply?) by trapdoor permutations \cite{bmw03}.
GS imply one-way functions \cite{romp90}.
GS imply public key encryption \cite{aw04}.
Commitments from group signatures (group signatures imply commitments?)
(ref. 25 in \cite{bfg+11}).

@@

\subsection{Further Notes}
\note{Integrate this section or delete it.}

\todo{CCA2 type of anonymity is defined in \cite{bbs04}. Schemes with CPA type
  of anonymity are (according to \cite{ehk+19}): \cite{bw06,bw07}.}

\cite{ehk+19} has a nice related work mentioning the assumptions that are
typically used.

Signature highjacking attacks (referenced in \cite{ehk+19}).

If we want to have traceability, the issuer needs to be honest. See what
implications this has in practice (e.g., what architectures are compatible
with this?) This probably makes schemes with separate issuing and opening
authorities more attractive in practice.

Other minor variants: group blind signatures, democratic group signatures,
mediated group signatures. All referenced in \cite[Section 1.3.5]{bsi12}.

Backward linkability property of group signatures with Timed Verifier-Local
Revocation, proposed in \cite{nf05}. Mentioned in \cite[Section 8.1.2]{bsi12}.

Relation of forward security with proactive security \cite{oy91}?

References 1, 24, 32 and, probably, 35 in \cite{bfg+11} seem to be (traceable)
group signatures that use the nym approach (or similar) for linking. Check.

\paragraph{Academic indicators.}
IACR, Esorics, CCS, AsiaCCS, SP, EuroSP, Usenix Sec and Privacy, PETs... Not
sure where to fit this.

Main cryptographic building blocks:

\begin{itemize}
\item BB signatures \cite{bb04}.
  \begin{itemize}
  \item Used in: \cite{ky05}.
  \item Paillier encryption of discrete-logarithms? Used in \cite{ky05} and,
    I think, \cite{gl19}.    
  \end{itemize}
\item Model for reduction: list of group signature schemes based on RO and
  non-RO are given in \cite{bcc+16}.
\end{itemize}

>>>>

\paragraph{Main intuition.}
%
Group signatures were first proposed by Chaum and van Heyst in 1991 \cite{ch91}
as a privacy-respectful extension to conventional digital signatures.
The intuition is simple: in order to avoid revealing the identity of the signer,
we make her signatures look indistinguishable to the signatures of all other
members of a group. Then, any entity with access to the group public key can
verify that a group signature comes from a member of the group, but cannot
tell which specific one actually created it.
%
Beyond this, group signature schemes have one main feature: a (set of) group
manager(s) control who can become a member of the group. Also, most frequently,
a (set of) group manager(s) decide when to expell a member from the group, or
when to re-identify the creator of a specific signature.
%
The initial idea put forward in \cite{ch91} had, as is to be expected, a number
of limitations. In the following years, the seminal work was extended, both
formally, functionally, and efficiency-wise.

@@

\subsubsection{Main approaches.}
%
There are two main ways that are recurrently used to instantiate group signature
schemes: \emph{Sign-Encrypt-Prove} and \emph{Sign-Randomize-Prove}. In both
variants, when new members of the group join, they receive a credential (i.e.,
a signature by the issuer) derived from a secret they choose. Then, when
creating a group signature, they prove control a valid credential and the
associated secret. The difference lies on how this credential is kept hidden
from the verifier.
%
In the sign-encrypt-prove variant, proposed in \cite{bmw03}, signers
encrypt their credential and then
create a NIZK \needcite proof of knowledge of such a valid credential
over their secret (plus the message they want to sign). This typically results
in schemes with more efficient openings, as the opening authority just has
to decrypt the encrypted credential. However, group signatures require more
space.
%
In the sign-randomize-prove variant, proposed in \needcite \todo{Get Shorty?},
credentials are actually randomizable signatures by the issuer. Signers then
randomize the signature (credential), and create a NIZK proof of knowledge that
this credential is issued for a secret they know (again, plus the message
they want to sign). This usually results in schemes with less efficient openings,
as the opening authority needs to iterate over the registered credentials until
finding the one from which the randomized credential was derived. However, the
produced group signatures are also shorter.

@@

\subsubsection{Main security models.}
%
Security for group signatures is given in the form of game-based definitions.
The first formal security model appeared in \cite{bmw03}. It captured security
for groups with a prefixed set of members, added by the group manager upon the
creation of the group. This static requirement was too restrictive to be
realistic, and was quickly extended in \cite{bsz05} and \cite{kty04,ky06}, to
model that new users can join the group after it has been created. The models
in \cite{bsz05,kty04,ky06} are usually referred to as dynamic or partially
dynamic. \cite{bcc+16} generalizes the (partially) dynamic setting into a fully
dynamic model, which considers extra desirable security properties when users
can be revoked (i.e., removed from the group).

@@

\paragraph{Forward security.}
Forward security aims at restricting the impact of security compromises (e.g.,
key leakage) to the future: i.e., if an attacker gains control of a user's
private key, only signatures produced after the compromise should be considered
invalid. In schemes that do not ensure forward secrecy, such a compromise also
renders invalid signatures produced before the compromise. Note that, for
conventional signatures, only the compromised user is (directly) affected by
such event. However,  in group signatures, all group members are directly
affected, as the signer's identity is not revealed by the signature. Thus,
in order to learn whether or not a past signature was issued by a compromised
user, it is necessary to resort to the opener -- therefore, reidentifying
\emph{all} users in the system.
%
Forward security has been introduced in group signatures in works like
\cite{song01,ly12}.
%
Interestingly (but logically), the approach to incorporate this property
holds similarities with the functionality to implement fully dynamic group
signatures: for forward security, users are usually required to apply an
update procedure to their private keys \cite{ly12}; in fully dynamic group
signatures \todo{fully dynamic gs have not been introduced yet!}, it is the
group manager (or the opener) who has to update some
key material \cite{bcc+16}. In both cases, time has to be discretized in epochs,
and conditions are introduced into the security properties that prevent an
adversary being able to deanonymize (produce) a valid signature generated
(using) a key in an epoch in which such key was not supposed to be active
(either because the user updated it -- in a forward secure scheme -- or the
group manager revoked it -- in a fully dynamic scheme).

\paragraph{\todo{Revocation mechanisms}.}
Verifier Local Revocation \cite{bs04}, accumulators approach.

@@

\begin{itemize}
\item Size of (group) keys.
\item Size of signatures.
\item Verification time (batching, including revocation checks...)
\end{itemize}

\subsubsection{Main challenges and interesting lines of work.}

@@

\begin{itemize}
\item GS-MDO imply IBE \cite{ehk+19}.
\item GS are implied by trapdoor permutations \cite{bmw03}.
\item GS imply one-way functions \cite{romp90}.
\item GS imply public key encryption \cite{aw04}.
\item Commitments from GS (ref. 25 in \cite{bfg+11}).
\end{itemize}

@@
